Men and Women Both Prefer and Perceive Inaction as More Competent

### 2024-02-16 outputs/paper/paper.qmd
paper update

The Data section of this report aims to discuss the characteristics of the Study 2 data set examined in addition to the methods of cleaning applied to get workable data for this report. This report’s Results section highlights trends discovered through graphical analysis in tandem with statistical analysis of the preference and perceived competence responses using t-tests and p-values to determine statistical insignificance. The Discussion section notes possible analytical limitations and measurement errors in the data sets in addition to overall insights of the report’s analysis. Specific discussion will surround the validity of assigning utilitarianism as a trait of men in addition to addressing whether or not there are differences in decision-making approaches based on gender. To summarize the report’s content, the Conclusion section briefly touches on the overall insights on moral judgment and gender that can be distilled from the findings of this report.

## Data
### Data Description

@@

## Results

@@

As seen when viewing @fig-preferencboth, 0 appears to be the most popular response from men which would indicate that a plurality of  study participants did not have a preference between action and inaction agents. However, the bar graph also shows that responses do seem to skew more towards the left or negative numeric value side which could imply that there is a general trend of men preferring inaction rather than action. Similarly, for women 0 appears to be the most popular response from graphical interpretation as seen in @fig-preferenceboth. While it does appear that more women gave a positive numeric value, therefore indicating preference for action, the overall graph does seem to also skew more to the left side. Since there were just over two times the amount of women study participants, it is possible the graph seems to reflect more preference towards action due to an increased amount of data points.

@@

## Discussion
### Report Findings
In Fillion, Stauch, and Feldman’s original article, they sought to examine the preference and perceived competence of action and inaction agents. They concluded that inaction agents are preferred and perceived as more competent [@giladpaper]. This report also replicates the findings in the original article since both men and women appear to prefer and perceive inaction agents as more competent based on analysis of the mean values from the scale of -5 to 5. However, this report also finds that both men and women have a trend towards preferring and perceiving inaction agents as more competent. Therefore, it can also be stated that this report found there to be no major differences in the perception of action and inaction agents between genders. This report also finds that there is no indication that women are more likely to be influenced by moral norms in decision-making on a statistical level.

@@

## Future Research
Since this paper found that decision-making perceptions did not vary vastly between gender, it would be worthwhile to investigate other factors that could influence decision-making. Looking towards the broader literature in the field, “Exploring cultural and gender differences in moral judgment: A cross-cultural study based on the CNI model” had similar findings on gender that concluded that gender did not have a significant effect on preference towards inaction. This article also delved deeper into research concerning whether or not an individual’s cultural positionality had an impact on moral judgment [@culturepaper]. This would be a worthwhile avenue to explore further in discerning the factors that influence decision-making since this study found there were differences based on cultural axes.

>>>>

[@sec-data] of this report aims to discuss the characteristics of the Study 2 data set examined in addition to the methods of cleaning applied to get workable data for this report. This report’s [@sec-results] highlights trends discovered through graphical analysis in tandem with statistical analysis of the preference and perceived competence responses using t-tests and p-values to determine statistical insignificance. [@sec-discussion] notes possible analytical limitations and measurement errors in the data sets in addition to overall insights of the report’s analysis. Specific discussion will surround the validity of assigning utilitarianism as a trait of men in addition to addressing whether or not there are differences in decision-making approaches based on gender. {@sec-future} aims to explore further research that could be conducted in this field based on the findings presented in this report.

## Data {#sec-data}
### Data Description

@@

## Results {#sec-results}

@@

As seen when viewing @fig-preferenceboth, 0 appears to be the most popular response from men which would indicate that a plurality of  study participants did not have a preference between action and inaction agents. However, the bar graph also shows that responses do seem to skew more towards the left or negative numeric value side which could imply that there is a general trend of men preferring inaction rather than action. Similarly, for women 0 appears to be the most popular response from graphical interpretation as seen in @fig-preferenceboth. While it does appear that more women gave a positive numeric value, therefore indicating preference for action, the overall graph does seem to also skew more to the left side. Since there were just over two times the amount of women study participants, it is possible the graph seems to reflect more preference towards action due to an increased amount of data points.

@@

## Discussion {#sec-discussion}
### Report Findings
In Fillion, Stauch, and Feldman’s original article, they sought to examine the preference and perceived competence of action and inaction agents. They concluded that inaction agents are preferred and perceived as more competent [@giladpaper]. This report also replicates the findings in the original article since both men and women appear to prefer and perceive inaction agents as more competent based on analysis of the mean values from the scale of -5 to 5. However, this report also finds that both men and women have a trend towards preferring and perceiving inaction agents as more competent. Therefore, it can also be stated that this report found there to be no major differences in the perception of action and inaction agents between genders. This report also finds that there is no indication that women are more likely to be influenced by moral norms in decision-making on a statistical level.

@@

## Future Research {#sec-future}
Since this paper found that decision-making perceptions did not vary vastly between gender, it would be worthwhile to investigate other factors that could influence decision-making. Looking towards the broader literature in the field, “Exploring cultural and gender differences in moral judgment: A cross-cultural study based on the CNI model” had similar findings on gender that concluded that gender did not have a significant effect on preference towards inaction. This article also delved deeper into research concerning whether or not an individual’s cultural positionality had an impact on moral judgment [@culturepaper]. This would be a worthwhile avenue to explore further in discerning the factors that influence decision-making since this study found there were differences based on cultural axes.
